On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-03-29 Manuscript/manuscript.tex
Manuscript Update 3/29

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$ blocks
of $Z_j$'s with replacement and then aligning them in the order they were picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}. The larger set of available blocks was used.
\jy{what does the last sentence mean?}

@@

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. A $(1 - \alpha)$ CI is
\[
(\hat{\theta}_{n} + \delta^*_{\alpha/2},
\hat{\theta}_{n} + \delta^*_{1 - \alpha/2}).
\]
\jy{Define $\delta^*$?}
\jy{Say a few words about its properties}

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
The $1 - \alpha$ \% BCA CI takes the form:
\[
(\hat{\theta}_{n} + \delta^*_{\alpha_1},
\hat{\theta}_{n} + \delta^*_{\alpha_2}),
\]
\jy{Not clear and not flowing well. Restructure the writing. Practice my writing tips.}
where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$ and
$z_{2}$, respectively, where:
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}.\]
Where $z_0$ is the quantile function of the proportion of
$\hat\theta_n^{(b)} < \bar\theta_n^{(b)}$, and $a$ is the skewness (computed
using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block.
\jy{Say a few words about its properties.}

@@

\jy{Make it flow better and conciser}
Each interval either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% CIs constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

To summarize, the interval type chosen should be based on the target parameter.
For estimating $\mu$, any of the three interval types can be used, but for
$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
for $\phi$. When estimating
$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
$\phi$, $n = 200$ is large enough when using the correct type of interval.

>>>>

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - b + 1$. Now we draw $k$ blocks from the $(n - b + 1)$
blocks
of $Z_j$'s with replacement and then aligning them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. Moving block bootstrap was used in
this study as it has been found to yield the lowest error in general
\citep{radovanov2014comparison}.  
\jy{what does the last sentence mean?}

@@

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval is
dependent on $\delta^{(b)}$, or the difference between a bootstrap point
estimate $\hat\theta_n^{(b)}$ and
the mean of all bootstrap point estimates.
 A $(1 - \alpha)$ CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2},
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is asymmetric, as different critical values are used to compute
the lower and upper bounds.
\jy{Define $\delta^*$?}
\jy{Say a few words about its properties}

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
In this study, the BCA CI is an interval centered at the point estimator.
However, unlike the Centered Percentile CI, which uses the simpler $\alpha/2$
and $1 - \alpha/2$ critical values, a more complex procedure is used to get
the critical values for the BCA CI. The first step is to compute $z_0$, the
quantile function of the proportion of 
$\hat\theta_n^{(b)} < \hat\theta_n$, and $a$, the skewness (computed
using
the skewness function from the R e1071 package \citep{e1071}) of
$\hat{\theta}_{n, -i}$, where $\hat{\theta}_{n, -i}$ is the statistic of the
original sample computed without the $i^{th}$ block. From these two values,
\[z_{1} = \frac{z_{0} - z_{1 - \alpha/2}}{1 - a(z_{0} - z_{1 - \alpha/2})} +
z_{0}\] and
\[z_{2} = \frac{z_{0} + z_{1 - \alpha/2}}{1 - a(z_{0} + z_{1 - \alpha/2})} +
z_{0}\] can be computed.

The $1 - \alpha$ \% BCA CI takes the form:
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha_1},
\hat{\theta}_{n} + \delta^{(b)}_{\alpha_2}),
\]
\jy{Not clear and not flowing well. Restructure the writing. Practice my
  writing tips.}
where $\alpha_{1}$ and $\alpha_{2}$ are the cumulative probability of $z_{1}$
and
$z_{2}$, respectively.
Like the Centered CI, the BCA CI is asymmetric.

\jy{Say a few words about its properties.}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. To
compute a CI's coverage rate of a target parameter for a certain interval,
the coverage for each replicate CI must be recorded. If the true value of the
parameter is greater than the lower bound of the CI and lesser than the upper
bound, then the CI's coverage for that parameter is assigned a value of 1. If
this is false, then the CI's coverage for that parameter is assigned a value
of 0.

Remember that 95\% of many of a certain type of 95\% CIs constructed from
samples of the same $n$ should recover a target $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and the proportion of replicate CIs that recover $\theta$ - or the
mean of the coverages for each replicate CI - can be
recorded as the coverage rate. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 1000$) can be constructed. If the proportion
.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

To summarize, the CI type chosen should be based on the target parameter.
For estimating $\mu$, any of the three interval types can be used, but for
$\sigma$, only $\hat{\theta}_{n}$-centered and basic percentile intervals
should be used, and only $\hat{\theta}_{n}$-centered intervals should be used
for $\phi$. When estimating
$\mu$, $n = 500$ should be large enough in situations where $\phi$ is unknown.
When estimating $\sigma$, $n = 400$ is sufficient is situations where $\phi$ is
unknown. If $\phi$ is known, a lesser $n$ may be adequate. When estimating
$\phi$, $n = 200$ is large enough when using the correct type of interval.
